Precise predictions for same-sign W-boson scattering at the LHC

### 2018-03-08 Draft/scanNLO.tex
Typos corrected scanNLO.tex

We compare three different predictions at NLO QCD: 
the VBS approximation (dubbed $|t|^2+|u|^2$) implemented in {\sc Bonsay}, the VBS approximation with the $s$-channel contributions from {\sc VBFNLO} (dubbed $|s|^2+|t|^2+|u|^2$), and the full computation.
The full computation employs full matrix elements meaning that $t/u/s$ interferences, factorisable, and non-factorisable QCD corrections as well as EW corrections to the order $\mathcal{O}(\alphas \alpha^5)$ are included.
% This means that in order to cancel all IR singularities, also EW correction to the $\mathcal{O}(\alphas\alpha^5)$ interference have to be included \cite{Biedermann:2016yds}.

@@

Concerning leptonic observables, we show in Fig.~\ref{fig:mjjdyjj_1d_3} the distributions in the di-lepton invariant mass and in the Zeppenfeld variable of the electron, defined as
%
\begin{equation}
%  z_{\Pe^+} = \frac{y_{\Pe^+}-\frac{y_{\Pj_1}+y_{\Pj2}}2}{|y_{\Pj_1}-y_{\Pj_2}|} \,.
  z_{\Pe^+} = \frac{y_{\Pe^+}-\frac{y_{\Pj_1}+y_{\Pj2}}2}{|\Delta y_{jj}|} \,.
  \label{eq:Zeppenfeld}
\end{equation}
%
Analogous definitions will later also be used for the Zeppenfeld variable of the muon and of the third jet.
%
\begin{figure*}[hbt]
\centering
{\includegraphics[scale=0.35]{figures/scanfigures/mll_nlo.pdf}}
{\includegraphics[scale=0.35]{figures/scanfigures/zel_nlo.pdf}}
\caption{Differential distributions in the lepton-lepton invariant mass (left) and the electron Zeppenfeld variable (right) at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the full computation and two approximations.
The upper plots provide the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
In addition to the cuts of Sec.~\ref{subsec:inputpar}, the VBS cuts take the values $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.} 
\label{fig:mjjdyjj_1d_3}
\end{figure*}
%
The $|s|^2+|t|^2+|u|^2$ predictions for $m-{\rm e^+\mu^+}$ agrees rather well with the full curve, obtained from {\sc MoCa\-NLO+Recola}.
The prediction from {\sc Bonsay} is about $10\%$ lower around $1000 \GeV$.
% ; this discrepancy reaches about $20\%$ in the very high mass region. 
%The discrepancies are roughly constant over the whole spectrum.
% Instead, the right panel of Fig.~\ref{fig:mjjdyjj_1d_3} clearly shows that
The Zeppenfeld variable of the positron $z_e$ is more strongly affected by the exclusion of $s$-channels.
% with increasing negative discrepancy with respect to the full result at large values (up to $30\%$ for $z_{e^+}>1.2$).
% Including $s$-channels makes this discrepancy become positive, but smaller than $10\%$ over the whole spectrum.
% The muon observable $z_{\mu}$ behaves identically to the electron one, $z_e$.
For increasing $z_{\rm e}$, the $|t|^2+|u|^2$ approximation diverges from the full computation to reach about a $25\%$ difference  at $1.5$.
On the other hand, including $s$-channel contributions leads to a better approximation, staying within $10\%$ difference over the whole range.

>>>>

We compare three different predictions at NLO QCD: 
the VBS approximation (dubbed $|t|^2+|u|^2$) implemented in {\sc Bonsay}, the VBS approximation with the $s$-channel contributions from {\sc VBFNLO} (dubbed $|s|^2+|t|^2+|u|^2$), and the full computation.
The full computation employs full matrix elements meaning that $t/u/s$ interferences, factorisable and non-factorisable QCD corrections, as well as EW corrections to the order $\mathcal{O}(\alphas \alpha^5)$ are included.
% This means that in order to cancel all IR singularities, also EW correction to the $\mathcal{O}(\alphas\alpha^5)$ interference have to be included \cite{Biedermann:2016yds}.

@@

Concerning leptonic observables, we show in Fig.~\ref{fig:mjjdyjj_1d_3} the distributions in the di-lepton invariant mass and in the Zeppenfeld variable of the electron, defined as
%
\begin{equation}
%  z_{\Pe^+} = \frac{y_{\Pe^+}-\frac{y_{\Pj_1}+y_{\Pj2}}2}{|y_{\Pj_1}-y_{\Pj_2}|} \,.
  z_{\Pe^+} = \frac{y_{\Pe^+}-\frac{y_{\Pj_1}+y_{\Pj2}}2}{|\Delta y_{jj}|} \,.
  \label{eq:Zeppenfeld}
\end{equation}
%
Analogous definitions will later also be used for the Zeppenfeld variable of the muon and of the third jet.
%
\begin{figure*}[hbt]
\centering
{\includegraphics[scale=0.35]{figures/scanfigures/mll_nlo.pdf}}
{\includegraphics[scale=0.35]{figures/scanfigures/zel_nlo.pdf}}
\caption{Differential distributions in the lepton-lepton invariant mass (left) and the electron Zeppenfeld variable (right) at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the full computation and two approximations.
The upper plots provide the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
In addition to the cuts of Sec.~\ref{subsec:inputpar}, the VBS cuts take the values $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.} 
\label{fig:mjjdyjj_1d_3}
\end{figure*}
%
The $|s|^2+|t|^2+|u|^2$ predictions for $m_{\rm e^+\mu^+}$ agrees rather well with the full curve, obtained from {\sc MoCa\-NLO+Recola}.
The prediction from {\sc Bonsay} is about $10\%$ lower around $1000 \GeV$.
% ; this discrepancy reaches about $20\%$ in the very high mass region. 
%The discrepancies are roughly constant over the whole spectrum.
% Instead, the right panel of Fig.~\ref{fig:mjjdyjj_1d_3} clearly shows that
The Zeppenfeld variable of the positron $z_e$ is more strongly affected by the exclusion of $s$-channels.
% with increasing negative discrepancy with respect to the full result at large values (up to $30\%$ for $z_{e^+}>1.2$).
% Including $s$-channels makes this discrepancy become positive, but smaller than $10\%$ over the whole spectrum.
% The muon observable $z_{\mu}$ behaves identically to the electron one, $z_e$.
For increasing $z_{\rm e}$, the $|t|^2+|u|^2$ approximation diverges from the full computation to reach about a $25\%$ difference  at $1.5$.
On the other hand, including $s$-channel contributions leads to a better approximation, staying within $10\%$ difference over the whole range.
